\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {STEPHEN ONYANCHA}}\\
	Nairobi $\cdot$ stevenonyancha1@gmail.com $\cdot$ +254 701 38001 \\ %$\cdot$ www.impalatech.xyz\\
\end{center}

%==== Education ====%
\header{Education}

\textbf{Institute of Advanced Technology}\hfill Nairobi\\
Cert. CCNA \hfill 2017 - 2018\\
\vspace{2mm}
\textbf{Laikipia University}\hfill Nyahururu, Laikipia.\\
BSc Computer Science \textit{GPA: Second Class Honors} \hfill 2013 - 2017\\
\vspace{2mm}
\textbf{St. Mark\textquotesingle{}s High School}\hfill Cherangani, Trans Nzoia.\\
Cert. KCSE \textit{GPA: A-} \hfill 2009 - 2012\\
\vspace{2mm}
\textbf{Milimani Primary School}\hfill Kitale, TransNzoia.\\
Cert. KCPE \textit{GPA: B+ / 365} \hfill 2001 - 2008\\
\vspace{2mm}


%==== Experience ====%
\header{Work Experience}
\vspace{1mm}

\textbf{Simba Colt Motors} \hfill Mombasa Road, Nairobi\\
\textit{System Admin Intern} \hfill 2018 \\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item ICT support
	\item ERP Support and maintenance.
	\item Network support.
	\item hardware and software maintenance and troubleshooting
	
\end{itemize}
\textbf{Kenya Urban Roads Authority} \hfill Industrial Area, Nairobi.\\
\textit{Attache} \hfill2016\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item ICT Support
	\item Assisted in setting up KURA datacenter at Regional Office Industrial area; water detecting system, adding               	  	storage, router, switch to the rack, UPS installation.
	\item Hardware and software maintenance and troubleshooting
	
\end{itemize}
\textbf{Laikipia University} \hfill Nyahururu, Laikipia.\\
\textit{Internal Attache} \hfill 2015\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Oracle database administration
	\item Built school website as Individual Project us HTML, CSS, JavaScript and using MySQL Server with LAMP server.
	\item Linux administration overview
	\item Networking switching and routing configuration of devices and troubleshooting.
\end{itemize}

\header{Skills}
\begin{tabular}{ l l }
	Programming Languages:                                & Java, PHP, JavaScript, python, BASH \\
	Framework:                                & Laravel\\
	MySql database                                 & \\
	Linux Administration                                 & \\
	Cisco IOS and Huawei VRP.   & \\
	leadership, communication, and collaboration skills: &                           \\
	Cybersecurity                                     &                           \\
\end{tabular}
\vspace{2mm}

\header{Project}
{\textbf{Road Inspection Software Tool}} {\sl PHP, JavaScript, HTML, Mysql} \hfill https://github.com/steveonyancha/inspection.git\\
A software for collecting data during routine road maintenance works.\\
\vspace*{2mm}
{\textbf{Biometric Students Lecture Attendance Management System.}} {\sl PHP, JavaScript, HTML, MYSQL, VERI Finger API} \\
Group Project. System that tracks student lecture attendance.\\
\vspace*{2mm}

\header{Award}
\textbf{Introduction to Cybersecurity} \hfill Cisco Networking Academy\\
Certificate of Completion. \hfill 2017\\
\vspace*{2mm}
\textbf{Linux Essential} \hfill Cisco Networking Academy\\
Certificate of Completion \hfill 2017\\
\vspace*{2mm}

\ 
\end{document}